---
title: "Associations Between Cognitive Appraisals and Emotions: A Meta-Analytic Review (Interactive Applet)"
author: "Gerard Yeo & Desmond Ong"
date: "1 June 2024"
output:
  html_document:
    theme: darkly
    highlight: tango
    df_print: paged
    code_folding: hide
  html_notebook:
    toc: yes
    toc_depth: '3'
fontsize: 16pt
runtime: shiny
---



```{r preamble, echo=T, message=F, warning=F}
# import libraries for meta-analysis
library(metaSEM)
library(mvmeta)
library(metafor)
library(tidyverse)
library(psych) # to convert z to r using fisherz2r(meta_df$b[1])
library(bslib)
library(pander)

my_theme <-  theme_bw() + theme(legend.position="top",
                                strip.background = element_rect(fill="#FFFFFF"), 
                                strip.text = element_text(size=12), 
                                axis.text = element_text(size=12),
                                axis.title.x = element_text(size=14, vjust=-0.2),
                                axis.title.y = element_text(size=14, vjust=0.8),
                                legend.text = element_text(size=12),
                                title = element_text(size=18, vjust=1),
                                panel.grid = element_blank())

```


This R Shiny application is an accompaniment to the following paper:

Yeo, G. C., & Ong, D. C. (to appear). Associations Between Cognitive Appraisals and Emotions: A Meta-Analytic Review. <i>Psychological Bulletin</i>.

The GitHub repository can be found at: https://github.com/desmond-ong/appraisal-meta-analysis



This application provides an interactive UI on which to query our data. In particular, we provide "interactive" versions of the large Tables in our paper, and you can click on the various options to filter (subset) specific emotions or appraisals of interest.

To run this application locally, we recommend using RStudio. When you load this file in RStudio, it would prompt you to install any packages you need (including knitr, shiny, etc). Then just hit "Run Document" in the top bar to launch!


```{r read-in-data-and-cleaning, echo=T, message=F, warning=F}
## -- This chunk reads in the data and defines the emotions/appraisals -- ##

data <- read.csv('meta-analysis_data.csv',header=T) %>%
  filter(included=="yes") %>%
  droplevels() %>%
  mutate(Appraisal_Raw = Appraisal)

### --- Cleaning emotions and appraisals ---- ####
# 47 appraisals, 63 emotions

LIST_OF_EMOTIONS_Short = c("anger", "anxiety", "boredom", "enjoyment", "fear", 
                           "guilt", "joy", "pride", "sadness", "shame")
LIST_OF_EMOTIONS_Long = c(
  "admiration", "affection", "amusement", "apathy", "awe", 
  "bitter", "challenge", "comfortable", "compassion", "confident", 
  "confusion", "contempt", "contentment", "curious", "disappointment", 
  "disgust", "distrust", "embarrassment", "empathy", "enthusiasm", 
  "envy", "excitement", "frustration", "gladness", "gratitude", 
  "homesickness", "hope", "inspiration", "interest", "irritation", 
  "jealousy", "loneliness", "longing", "love", "nostalgia", 
  "pity", "playfulness", "pleasure", "psyched-up", "regret", 
  "relief", "resignation", "schadenfreude", "self-anger", "self-pity", 
  "serenity", "surprise", "sympathy", "tenderness", "threat-awe", "unfriendly", 
  "unlucky", "worry")

# 
# "despair" in this study. Renamed as "hope". Effect sizes have been reversed coded.
# "relaxation" in study. Renamed to "serenity"
# "dejection" in this study. Renamed to "sadness"
# "humiliation" in the study. Renamed to "shame"
# "hopelessness" in study. Renamed as "hope". Effect sizes have been reversed coded
# "positive surprise" in study. Renamed to "surprise"
# "satisfaction" in study. Renamed to "contentment".
# "liking" in study. Renamed as "affection"
# "hopeful" in study. Renamed to "hope"
# "nervous" in study. Renamed to "anxiety"
# "resentful" in study. Renamed to "bitter"
# "annoy" in this study. Renamed to "irritation"
# "tranquility" in study. Renamed to "serenity"
# 
# emotion measured as fearful/worry/anxiety, and we separate into fear, worry, and anxiety.
# emotion measured as hope/confidence, and we separate into hope and confident
# 
# "familiarity" in study. Reversed coded to "novelty".
# "immorality" in study. Reverse coded to merge with normative significance (external)
# "unexpectedness" in study. Re-coded to "expectedness"
# "irrelevance" in study. Reverse-coded to "goal relevance"

# some studies measured multiple appraisals within the same "cluster" (that we define).
# for these, we picked the most relevant one and excluded the rest.

LIST_OF_APPRAISALS = c(
  'pleasantness', 'threat', 'loss', 'harm', 'severity', "easing of threat", 
  
  'goal conduciveness', 'goal relevance', 'value', 'difficulty', 
  'perceived obstacle', 'attainability', 'desire for object', 
  
  'accountability-circumstances', 'accountability-other', 
  'accountability-self', 'intentionality', 
  
  'control-circumstances', "control-other", "control-self", 
  'emotion-focused coping potential', 'problem-focused coping potential', 
  'effortful success', "modifiability",
  
  'novelty', 'expectedness', "remarkable", 'uniqueness',
  
  'future expectancy', 'attentional activity', 'certainty',
  'future predictability', 'effort', 'stability', 
    
  'fairness', 'normative significance (external)', 'normative significance (internal)', 
  
  'concern for others', 'closeness', "evil character", "liking", 
   
  'challenge', 'globality', "reality", 
  "self-esteem decreased", 'temporal distance', 'vastness')

LIST_OF_APPRAISALS_alphabetical = LIST_OF_APPRAISALS[str_order(LIST_OF_APPRAISALS)]


# The following lines "groups" appraisals with different terminologies 
# into the appraisal "clusters" we have defined in the paper, i.e., 
# LIST_OF_APPRAISALS just above. 
data <- data %>%
  mutate(Appraisal = fct_collapse(Appraisal,
    'accountability-circumstances' = c("agency-circumstances",
                                       'circumstances-attribution', 
                                       'situational-agency',
                                       "situation-attribution"),
    'accountability-other' = c('agency-other', 'external agency',
                               'other-accountability',
                               'other-attribution', 'other-blame',
                               'other-caused',
                               'other-responsibility'),
    'accountability-self' = c("agency-self", 'internal agency', 
                              "internal attribution", "internal locus",
                              'self-accountability', 'self-attribution',
                              'self-blame', 'self-caused', 
                              'self-responsibility'),
    'attainability' = c('attainability', "possibility"),
    'attentional activity' = c('attention', 'attentional activity', 
                               'consideration', 'urgency', 'safety (reversed)'),
    'certainty' = c('certainty', 'clarity', 'understandability'),
    'challenge' = c('challenge'),
    'closeness' = c('closeness'),
    'concern for others' = c('other-concern', 'other-involved'),
    'control-circumstances' = c("circumstances-control", 'situational-control'),
    "control-other" = c( "control-other", 'external control'),
    "control-self" = c('control-self', 'personal control', 'power', 'helplessness (reversed)'),
    'desire for object' = c('desirability'),
    'difficulty' = c('difficulty', 'situational demand', 'skill demand'),
    "easing of threat" = c("easing of threat"),
    'effort' = c('effort'),
    'effortful success' = c('effortful optimism', "potential for success"),
    'emotion-focused coping potential' = c('emotion-focused coping potential'),
    "evil character" = c('evil character'),
    'expectedness' = c('expectation', 'expectedness'),
    'fairness' = c("deservingness", "fairness" ,'injustice (reversed)', 
                   "justice", 'legitimacy', 'unfairness (reversed)'),
    'future expectancy' = c("future expectancy", 
                            "future expectations", "positive future expectancy", 
                            "negative future expectancy",
                            "outcome expectancy", "optimism", "expected success", "negative likelihood (reversed)"),
    'globality' = c('globality'),
    'goal conduciveness' = c('benefit',  
                             'goal conduciveness',
                             'goal congruence', 
                             'goal hindrance (reversed)', 'motivational congruence',
                             "motivational consistency",
                             'situational state', 'hindrance (reversed)'),
    'goal relevance' = c('centrality', 'goal relevance',
                         'importance',
                         'motivational relevance', "self-concern"),
    'harm' = c('harm'),
    'intentionality' = c('other-intentionality', 'intentionality'), 
    "liking" = c("liking"),
    'loss' = c('loss', 'reversibility (reversed)'),
    "modifiability" = c("modifiability"),
    'normative significance (external)' = 
      c('external self-compatibility', 'fail to live up to external standards (reversed)',
        'norm compatibility', 'norm violation (reversed)',
        "compatibility with external standards norms"),
    'normative significance (internal)' = 
      c("compatibility with individual norms", 
        "compatibility with internal standards",
        "internal self-compatibility", "moral congruence", "self-consistency",
        "immorality (reversed)"),
    'novelty' = c('novelty', "familiarity (reversed)"), 
    'perceived obstacle' = c('obstacle','problems'),
    'pleasantness' = c('intrinsic pleasantness', 'pleasantness', 'valence'),
    'future predictability' = c('predictability', "outcome probability"),
    'problem-focused coping potential' = c('competence', 'coping potential', 
                                           'problem-focused coping potential', 
                                           'self-efficacy'),
    "reality"  = c("reality"),
    "remarkable" = c('remarkable', 'exceed expectation'),
    "self-esteem decreased" = c("self-esteem decreased"),
    'severity' = c("impact", "severity"),
    'stability' = c('stability'),
    'temporal distance' = c('temporal distance'),
    'threat' = c('threat', 'danger', 'risk', "susceptibility", 'vulnerability'),
    'uniqueness' = c('uniqueness', 'pattern/unique'),
    'value' = c('attainment value', 'intrinsic value', 'outcome value','value'),
    'vastness' = c('vastness')
  )) %>% mutate(Appraisal = fct_relevel(Appraisal, LIST_OF_APPRAISALS),
                Emotion = factor(Emotion),
                Appraisal_alphabetical_order = fct_relevel(Appraisal, LIST_OF_APPRAISALS_alphabetical))



## The rows with the following emotions are not included in meta-analysis 
##   (reasons are given in the remarks column)
## These emotions are already tagged with "no" in the `included` column
##   and so are already excluded by the above data read-in.
# LIST_OF_EMOTIONS_NOTUSED = c("depression", "stress", "beloved", "embrace", 
#                              "grief", "hate", "hostility", "melancholy", "rage")

## similarly the following appraisals are not included. 
# LIST_OF_APPRAISALS_NOTUSED = 
#   c("ability", # consists of multiple appraisals, stable and uncontrollable
#     "causal locus", # this study also measured 'other-accountability', which is
#                     # more relevant
#     "coping ability", # this study measured on a nominal scale; 
#                       # each level had a different anchor point
#     "external causation", # one study measured on nominal scale
#                           # another study included 'other person' and 'external'
#                           # and one study used factor scores
#     "external locus", # for this study, unclear whether 'other person' or 'external'
#     "extrinsic value", # this study had both 'intrinsic' and 'extrinsic'
#                        # we chose to use intrinsic
#     "locus of causality", # unclear whether 'other person' or 'external'
#     "obstacle/effort", # consists of multiple appraisals
#     'other-significance', # excluded because this study also has 'other-concern'
#     "uncontrollable", # unclear in the study's definition.
#     "valued achievement", # multiple appraisals: "accountability-self", 
#                          # and "goal conduciveness"
#     "other-caused failure", "other-caused success",
#     "self-caused failure", "self-caused success")

```

```{r helper-functions, echo=T, eval=T}

## --- This chunk contains helper-functions to compute the meta-analysis, 
## publication bias analyses, and other functions for creating the tables. 
## -- ##


# P-curve analysis
# The following are the auxiliary and main functions used to run 
# the p-curve analysis. I adapted the code from the original authors -
# http://p-curve.com/app4/pcurve_app4.06.r

# Function 1 - functions that find non-centrality parameter for f,chi 
#    distributions that gives some level of power
# F-test 
# Note: starting with app 4.0, t() are converted to F() and Z to chisq() to 
#      avoid unnecessary repetition of code
# So we only need code to find ncp for F() and chisq()
getncp.f = function(df1,df2, power)   {      
  error = function(ncp_est, power, x, df1,df2) 
    pf(x, df1 = df1, df2=df2, ncp = ncp_est) - (1-power)   
  xc=qf(p=.95, df1=df1,df2=df2) 
  return(uniroot(error, c(0, 1000), x = xc, df1 = df1,df2=df2, power=power)$root)  
}

# chisq-test
getncp.c =function(df, power)   {      
  xc=qchisq(p=.95, df=df) 
  error = function(ncp_est, power, x, df) 
    pchisq(x, df = df, ncp = ncp_est) - (1-power)   
  return(uniroot(error, c(0, 1000), x = xc, df = df, power=power)$root)   
}

# Combine both in single function
getncp = function(family,df1,df2,power) {
  if (family=="f") ncp=getncp.f(df1=df1,df2=df2,power=power)
  if (family=="c") ncp=getncp.c(df=df1,power=power)
  return(ncp)  
}

# Function 3 - pbound: bound p-values and pp-values by precision of 
#                     measurement to avoid errors
pbound=function(p) pmin(pmax(p,2.2e-16),1-2.2e-16)

# Function 4 - prop33(pc) - Computes % of p-values that are expected to be 
#                           smaller than pc, for the tests submitted to 
#                           p-curve, if power is 33%
prop33=function(pc, family1, p, r_df, ncp33)
{
  #pc: critical  p-value
  #Overview:
  #Creates a vector of the same length as the number of tests 
  #        submitted to p-curve, significant and not,
  #    and computes the proportion of p-values expected to be smaller than 
  #        {pc} given the d.f. 
  #    and outputs the entire vector, with NA values where needed
  # F-tests (& thus  t-tests)
  prop=ifelse(family1=="f" & p<.05,
              1-pf(qf(1-pc,df1=1, df2=r_df),df1=1, df2=r_df, ncp=ncp33),NA)
  # Chi2 (& thus Normal)
  prop=ifelse(family1=="c" & p<.05,
              1-pchisq(qchisq(1-pc,df=df1), df=df1, ncp=ncp33),prop)
  # output it
  prop
}

# Function 5 Stouffer test for a vector of pp-values
stouffer=function(pp) sum(qnorm(pp),na.rm=TRUE)/sqrt(sum(!is.na(pp)))

# main p-curve function. This function takes in a dataframe 
#          (that has already been subsetted by the appraisal and emotion) 
#          and computes the necessary p-curve statistics
p_curve = function(df) {
  r_values <- df$r
  r_df = df$N - 2
  # Create family to turn t-->F
  family1 = rep("f",dim(df)[1])
  #For correlation, first turn value (r) to t, then square t. 
  #     (using t=r/sqrt(1-r**2)/DF)
  value= (r_values/(sqrt((1-r_values**2)/r_df)))**2
  # Compute p-values
  p = 1-pf(value,df1=1,df2=r_df)
  p=pbound(p) 
  # Count  studies
  ksig= sum(p<.05,na.rm=TRUE)     #significant studies
  khalf=sum(p<.025,na.rm=TRUE)  #half p-curve studies
  
  # COMPUTE PP-values
  #2.1 Right Skew, Full p-curve
  ppr=as.numeric(ifelse(p<.05,20*p,NA))            
  #If p<.05, ppr is 1/alpha*p-value, so 20*pvalue, otherwise missing. 
  ppr=pbound(ppr)      #apply pbound function to avoid 0
  
  #2.2 Right Skew, half p-curve
  ppr.half=as.numeric(ifelse(p<.025,40*p,NA))    
  #If p<.05, ppr is 40*pvalue, otherwise missing. 
  ppr.half=pbound(ppr.half)
  
  #2.3 Power of 33%
  #2.3.1 NCP for  f,c distributions
  # NCP33 (noncentrality parameter giving each test 
  #    in p-curve 33% power given the d.f. of the test)
  ncp33=mapply(getncp,df1=1,df2=r_df,power=1/3,family=family1) 
  #See function 1 above
  
  #2.3.2 Full-p-curve
  #Using the ncp33 compute pp33
  pp33=ifelse(family1=="f" & p<.05,3*(pf(value, df1=1, df2=r_df, ncp=ncp33)-2/3),NA)
  pp33=pbound(pp33)
  
  #2.3.3 HALF-p-curve
  #Share of p-values expected to be p<.025 if 33% power 
  #   (using Function 4 from above, prop33() )
  prop25=3*prop33(.025, family1 = family1, p = p, r_df = r_df, ncp33 = ncp33 )
  prop25.sig=prop25[p<.05]
  
  #Compute pp-values for the half
  pp33.half=ifelse(family1=="f" & p<.025, (1/prop25)*(
    pf(value,df1=1,df2=r_df,ncp=ncp33)-(1-prop25)),NA)
  pp33.half=pbound(pp33.half)
  
  #########################################################################  
  # INFERENCE - STOUFFER & BINOMIAL
  ###########################################################################  
  
  # Convert pp-values to Z scores, using Stouffer function above
  Zppr =     stouffer(ppr)            #right skew  - 
                                      # this is a Z value from Stouffer's test
  Zpp33=     stouffer(pp33)           #33% - idem 
  Zppr.half= stouffer(ppr.half)       #right skew, half p-curve - idem 
  Zpp33.half=stouffer(pp33.half)      #33% skew, half p-curve - idem 
  
  # Overall p-values from Stouffer test
  p.Zppr =pnorm(Zppr)	
  p.Zpp33=pnorm(Zpp33)
  p.Zppr.half =pnorm(Zppr.half)
  p.Zpp33.half=pnorm(Zpp33.half)
  
  return(c(Zppr, p.Zppr, Zpp33, p.Zpp33, Zppr.half, p.Zppr.half))
}




### the following functions help to provide the interpretation
### of significant appraisal-emotion relationships

# These mappings just make the interpretation sound more grammatical.
emotion_strings = data.frame(
  emotion = c(LIST_OF_EMOTIONS_Short, LIST_OF_EMOTIONS_Long),
  string = c(LIST_OF_EMOTIONS_Short, 
    c("admiration", "affection", "amusement", "apathy", "awe", 
      "bitter", "challenge", "comfortable", "compassion", "confidence", 
      "confusion", "contempt", "contentment", "curiosity", "disappointment", 
      "disgust", 
      "distrust", "embarrassment", "empathy", "enthusiasm", "envy", 
      "excitement", "frustration", "gladness", "gratitude", "homesickness", 
      "hope", "inspiration", "interest", "irritation", "jealousy", 
      "feelings of loneliness", 
      "feelings of longing", 
      "love", "nostalgia", "pity", "playfulness", 
      "pleasure", "psyched-up", "regret", "relief", "resignation",  
      "feelings of schadenfreude", 
      "self-anger", "self-pity", "serenity", "surprise", 
      "sympathy", "tenderness", 
      "feelings of awe (in response to something threatening or fearful)",
      "feelings of unfriendliness", 
      "feelings of unluckiness", "worry"))
)


appraisal_strings = data.frame(
  appraisal = LIST_OF_APPRAISALS,
  string = c(
    'perceived pleasantness of the situation', 
    'perceived imminent threat in the situation', 
    'perception that something irretrievable has been lost', 
    'perceived harm', 
    "perceived severity of the consequences of the situation to one's well-being", 
    "perception that a threat or harm has been removed from the situation", 
    
    "consistency of the situation with one's goals", 
    "perceived relevance of the situation to one's goals", 
    "perceived value of the situation to one's goals and desires",
    'perceived difficulty', 
    'perception that an obstacle hampers the attainment of a desired goal', 
    'perception that one could obtain what one desires', 
    'desire for something another person has', 

    'attribution of the cause of the situation to impersonal circumstances', 
    'perceived responsibility for the cause of the situation attributed to other people/objects', 
    'perceived personal responsibility of the cause of the situation', 
    'perceived intentionality of the cause of the event either by oneself or others', 
  
    'perception that impersonal circumstances have control over the situation', 
    "perception that other people/objects have control over the situation", 
    "perceived control over the situation", 
    'ability to emotionally cope and adapt to the situation', 
    'perceived ability to cope and adapt to the situation', 
    'perception that effort could make the situation better', 
    "perception that the situation could be modified", 
  
    'perceived novelty in the situation',  
    'expectation of the occurrence of the situation', 
    "feeling that it was remarkable to have gotten this outcome", 
    'perception of how unique the situation was', 
  
    'expectation that the situation will get better',
    'perceived need to take time/effort to attend to the situation further', 
    'understanding of the situation', 
    'ability to predict what is going to occur in the future', 
    'need to exert effort to deal with the situation', 
    'perception that the situation is stable and permanent', 
  
    'perceived fairness of the situation', 
    'consistency of the situation with external and social norms',
    "consistency of the situation with one's ideals", 
  
    "concern for others' well-being in the situation", 
    'perception of closeness of the relationship to another person', 
    "perception of others as dispositionally evil", 
    "liking for another person", 
  
    'perception of a future gain after overcoming an obstacle in the situation', 
    "perception that the event is relevant to all aspect of one's life", 
    "perception that is situation is real and had already occurred", 
  "perception that one's self-esteem has decreased", 
  'perceived temporal distance to a remembered past situation', 
  "perception that something is much grander than oneself"
  )
)


# function that returns a grammatical string for the table
return_interpretation = function(this_appraisal, this_emotion, r) {
  # Example interpretation:
  # The greater the 
  # perceived responsibility for the cause of the 
  #     situation attributed to other people/objects
  # , the 
  # greater 
  # the 
  # anger
  
  appraisal_string = appraisal_strings[
    appraisal_strings$appraisal==this_appraisal, "string"]
  emotion_string = emotion_strings[
    emotion_strings$emotion==this_emotion, "string"]
  if(r>0) {comparator = "greater"} else {comparator = "less"}
  
  interpretation_string = paste(
    "The greater the ", 
    appraisal_string, 
    ", the ", comparator, " the ",
    emotion_string, ".", sep=""
  )
  return(interpretation_string)
}

```

```{r make-table-function, echo=T, eval=T}

# This function is a helper function to construct Results Tables
#   (Meta-analysis for a given Emotion and Appraisal)
#   It takes in the data frame and produces the necessary statistics
#   as a row of a data frame.
meta_analysis_for_table = function(df, this_emotion, 
                                   num_digits=4, 
                                   pubBias = TRUE, 
                                   interpretation=TRUE) {
  meta_df = rma(z,v,data=df, method = 'ML')
  
  if(meta_df$pval<0.001) {
    pstring = "***"
  } else if(meta_df$pval<0.01) {
    pstring = "**"
  } else if(meta_df$pval<0.05) {
    pstring = "*"
  } else { pstring = "" }
  
  table_df = data.frame(
      Emotion = this_emotion,
      Appraisal = df$Appraisal[1],
      k = nrow(df),
      # apply fisherz2r()
      r = paste(format(fisherz2r(meta_df$b[1]), digits=num_digits), 
                pstring, sep = ""))
  
  if(nrow(df)>1) {
    if(meta_df$QEp<0.001) {
      Q_pstring = "***"
    } else if(meta_df$QEp<0.01) {
      Q_pstring = "**"
    } else if(meta_df$QEp<0.05) {
      Q_pstring = "*"
    } else { Q_pstring = "" }
    
    table_df = table_df %>% mutate(
      # 95% CI; apply fisherz2r()
      ci = paste(format(fisherz2r(meta_df$ci.lb), digits=num_digits), 
                 format(fisherz2r(meta_df$ci.ub), digits=num_digits), sep=", "),
      # Q statistic, (Q df), Q_pstring
      Q = paste(format(meta_df$QE, digits=num_digits), " (", 
                format(nrow(df) - 1, digits=num_digits), ")", Q_pstring, sep=""),
      # sqrt(tau^2)
      #tau2 = format(meta_df$tau2, digits=num_digits),
      tau = format(sqrt(meta_df$tau2), digits=num_digits),
      # I2
      I2 = format(meta_df$I2, digits=num_digits))
  } else {
    table_df = table_df %>% mutate(ci = NA, Q = NA, tau = NA, I2 = NA)
  }
  
  
  # the publication bias analyses only done if 10 or more studies. 
  if(pubBias & nrow(df)>10) {
    reg_test = regtest(meta_df, model='rma')
    # fsn_orwin = fsn(yi=z, vi=v, data=df, type='Orwin', target=0.05)  
    # p_curve_results = p_curve(df)
    # ## p-curve significance
    # ## z_half
    #   if(p_curve_results[6]<0.001) { pstring1 = "***"
    #   } else if(p_curve_results[6]<0.01) { pstring1 = "**"
    #   } else if(p_curve_results[6]<0.05) { pstring1 = "*"
    #   } else { pstring1 = "" }
    # 
    # ## z_full
    #   if(p_curve_results[2]<0.001) { pstring2 = "***"
    #   } else if(p_curve_results[2]<0.01) { pstring2 = "**"
    #   } else if(p_curve_results[2]<0.05) { pstring2 = "*"
    #   } else { pstring2 = "" }
    # 
    # ## z_flat
    #   if(p_curve_results[4]<0.001) { pstring3 = "***"
    #   } else if(p_curve_results[4]<0.01) { pstring3 = "**"
    #   } else if(p_curve_results[4]<0.05) { pstring3 = "*" 
    #   } else { pstring3 = "" }
    
    
    table_df <- table_df %>% mutate(
      # Egger regression p value
      p_egger = format(reg_test$pval, digits=num_digits) #,
      ## fail-safe N
      #FSN = format(fsn_orwin$fsnum, digits=num_digits),
      ## z_half
      #z_half = paste(format(p_curve_results[5], digits=num_digits), 
      #          pstring1, sep = ""),
      ## z_full
      #z_full = paste(format(p_curve_results[1], digits=num_digits), 
      #          pstring2, sep = ""),
      ## z_flat
      #z_flat = paste(format(p_curve_results[3], digits=num_digits), 
      #          pstring3, sep = ""),
    )
  } else if (pubBias) { # 9 or fewer studies but still want to print pubBias
    table_df <- table_df %>% mutate(
      p_egger = NA #, FSN = NA, z_half = NA, z_full = NA, z_flat = NA
    )
  }
  if(interpretation) {
    if(meta_df$pval<0.05) {
      table_df <- table_df %>% mutate(interpretation = 
        return_interpretation(df$Appraisal[1], this_emotion, fisherz2r(meta_df$b[1]))
        )
    } else {
      table_df <- table_df %>% mutate(interpretation = NA)
    }
  }
  
  return(table_df)
}




```


# Results Tables

## Table for emotions with higher evidence (Table S4 in paper)

```{r shiny-app-appraisal-table-high_evidence_emotions, echo=T}
shinyApp(

  ui = fluidPage(
    #theme = bs_theme(bootswatch = "darkly"),
    # App title ----
    titlePanel("Results of main analyses and bias analyses for emotions with high evidence (max k > 10)"),
    
    fluidRow(
      column(12,
             h3("Emotions in this table: Anger, Anxiety, Boredom, Enjoyment, Fear, Guilt, Joy, Pride, Sadness, Shame."),
      )
    ),
    
    fluidRow(
      column(3,
             selectInput("this_emotion", "Emotion",
                         choices = c("All Emotions", LIST_OF_EMOTIONS_Short),
                         selected = "anger")
      ),
      
      column(3,
             selectInput("this_appraisal", "Appraisal",
                         choices = c("All Appraisals", LIST_OF_APPRAISALS))
      ),
      
      column(6,
             c("Table Display Options"),
             checkboxInput("show_pub_bias", 
                           "Show Egger's Regression Results", 
                           value = FALSE),
             checkboxInput("show_interp", 
                           "Show interpretation (for significant results)", 
                           value = TRUE)
             )
    ),
    
    fluidRow(
      column(12,
             dataTableOutput("table")
      )
    )
  ),
  
  
  
  server = function(input, output) {
    output$table = renderDataTable({
      this_table = data.frame()
      
      if(input$this_emotion == "All Emotions") {# looping through All emotions
        for(this_emotion in c(LIST_OF_EMOTIONS_Short)) {
          
          
            if(input$this_appraisal == "All Appraisals") { # looping through All appraisals
              for(this_appraisal in c(LIST_OF_APPRAISALS)) {
                df = data %>% filter(Emotion == this_emotion,
                                     Appraisal == this_appraisal)
                if(nrow(df)>=1) {
                  this_table = bind_rows(this_table, 
                                         meta_analysis_for_table(df, this_emotion,
                                                                 pubBias=input$show_pub_bias,
                                                                 interpretation=input$show_interp))
                }
              }
            } else { # only for the given appraisal
              df = data %>% filter(Emotion == this_emotion,
                                   Appraisal == input$this_appraisal)
              if(nrow(df)>=1) {
                this_table = bind_rows(this_table, 
                                       meta_analysis_for_table(df, this_emotion,
                                                               pubBias=input$show_pub_bias,
                                                               interpretation=input$show_interp)
                )
              }
            }
          
        }
      } else { # only for the given emotion
        this_emotion = input$this_emotion
            if(input$this_appraisal == "All Appraisals") { # looping through All appraisals
              for(this_appraisal in c(LIST_OF_APPRAISALS)) {
                df = data %>% filter(Emotion == this_emotion,
                                     Appraisal == this_appraisal)
                if(nrow(df)>=1) {
                  this_table = bind_rows(this_table, 
                                         meta_analysis_for_table(df, this_emotion,
                                                                 pubBias=input$show_pub_bias,
                                                                 interpretation=input$show_interp))
                }
              }
            } else { # only for the given appraisal
              df = data %>% filter(Emotion == this_emotion,
                                   Appraisal == input$this_appraisal)
              if(nrow(df)>=1) {
                this_table = bind_rows(this_table, 
                                       meta_analysis_for_table(df, this_emotion,
                                                               pubBias=input$show_pub_bias,
                                                               interpretation=input$show_interp)
                )
              }
            }
        
      } # end emotion
      
      if(nrow(this_table) < 1) {
        this_table = data.frame(Output="appraisal not found")
      } else {
        this_table = this_table %>% arrange(Emotion, desc(k), Appraisal) %>% 
          rename(`Num Studies k` = k,
                 `Effect Size (Pearson r)` = r,
                 `95% Confidence Interval` = ci)
      }
      
      
    })
    
  },

  options = list(height = 800)
)
```

Note: k denotes number of studies, r denotes the mean effect size in Pearson correlation coefficient, 95% CI denotes the 95% confidence interval of the mean effect size, τ denotes the true between-studies variability, I2 denotes the ratio of true between-study heterogeneity to total variance observed, df refers to the degrees of freedom, p_egger denotes the p-value of the Egger Regression Test. The “Predictions and Findings” columns denotes whether the results were consistent with what previous literature has hypothesized; see text for description of categories. Within each emotion, the appraisals are sorted by k, then by alphabetical order. * p < .05; ** p < .01; *** p < .001


## Table for remainder of emotions (Table S5)

```{r shiny-app-appraisal-table-low_evidence_emotions, echo=T}
shinyApp(

  ui = fluidPage(
    # App title ----
    titlePanel("Results of main analyses for emotions with less evidence (max k<=10)."),
    
    fluidRow(
      column(3,
             selectInput("this_emotion", "Emotion",
                         choices = c("All Emotions", LIST_OF_EMOTIONS_Long),
                         selected = "admiration")
      ),
      
      column(3,
             selectInput("this_appraisal", "Appraisal",
                         choices = c("All Appraisals", LIST_OF_APPRAISALS))
      ),
      column(6,
             c("Table Display Options"),
             checkboxInput("show_interp", 
                           "Show interpretation (for significant results)", 
                           value = TRUE)
             )
    ),
    
    fluidRow(
      column(12,
             dataTableOutput("table")
      )
    )
  ),
  
  server = function(input, output) {
    
    output$table = renderDataTable({
      this_table = data.frame()
      
      
      if(input$this_emotion == "All Emotions") {# looping through All emotions
        for(this_emotion in c(LIST_OF_EMOTIONS_Long)) {
          
            if(input$this_appraisal == "All Appraisals") { # looping through All appraisals
              for(this_appraisal in c(LIST_OF_APPRAISALS)) {
                df = data %>% filter(Emotion == this_emotion,
                                     Appraisal == this_appraisal)
                if(nrow(df)>=1) {
                  this_table = bind_rows(this_table, 
                                     meta_analysis_for_table(df, this_emotion,
                                                             pubBias=FALSE,
                                                             interpretation=input$show_interp))
                }
              }
            } else { # only for the given appraisal
              df = data %>% filter(Emotion == this_emotion,
                                   Appraisal == input$this_appraisal)
              if(nrow(df)>=1) {
                this_table = meta_analysis_for_table(df, this_emotion,
                                                     pubBias=FALSE,
                                                     interpretation=input$show_interp)
              }
            }
          
        }
      } else {
        # only for the given emotion
        this_emotion = input$this_emotion
            if(input$this_appraisal == "All Appraisals") { # looping through All appraisals
              for(this_appraisal in c(LIST_OF_APPRAISALS)) {
                df = data %>% filter(Emotion == this_emotion,
                                     Appraisal == this_appraisal)
                if(nrow(df)>=1) {
                  this_table = bind_rows(this_table, 
                                     meta_analysis_for_table(df, this_emotion,
                                                             pubBias=FALSE,
                                                             interpretation=input$show_interp))
                }
              }
            } else { # only for the given appraisal
              df = data %>% filter(Emotion == this_emotion,
                                   Appraisal == input$this_appraisal)
              if(nrow(df)>=1) {
                this_table = meta_analysis_for_table(df, this_emotion,
                                                     pubBias=FALSE,
                                                     interpretation=input$show_interp)
              }
            }
        
      }
      
      
      
      
      
      if(nrow(this_table) < 1) {
        this_table = data.frame(Output="appraisal not found")
      } else {
        this_table = this_table %>% arrange(Emotion, desc(k), Appraisal) %>% 
          rename(`Num Studies k` = k,
                 `Effect Size (Pearson r)` = r,
                 `95% Confidence Interval` = ci)
      }
      
    })
    
  },

  options = list(height = 500)
)
```



## Reference Look Up

Use this next table to look up specific studies that studied a certain emotion and/or a certain appraisal. Note that emotions are listed alphabetically, and appraisals are listed thematically, according to our ordering in Table 1 in the main paper.

```{r shiny-app-looking-up-references, echo=T}
shinyApp(

  ui = fluidPage(
    # App title ----
    titlePanel("Use this app to lookup specific references"),
    
    fluidRow(
      column(6,
             selectInput("this_emotion", "Emotion",
                         choices = c("All Emotions", sort(c(LIST_OF_EMOTIONS_Short, LIST_OF_EMOTIONS_Long))))
      ),
      
      column(6,
             selectInput("this_appraisal", "Appraisal",
                         choices = c("All Appraisals", LIST_OF_APPRAISALS))
      )
    ),
    
    fluidRow(
      column(12,
             dataTableOutput("table")
      )
    )
  ),
  
  server = function(input, output) {
    
    output$table = renderDataTable({
      this_table = data.frame()
      df = data
      if(input$this_emotion != "All Emotions") {
        df = data %>% filter(Emotion == input$this_emotion)
      }
      if(input$this_appraisal != "All Appraisals") {
        df = data %>% filter(Appraisal == input$this_appraisal)
      }
        
        if(nrow(df)>=1) {
          this_table = df %>% 
            select(Study, Year, Appraisal, Emotion, Dissertation, r, z, remarks) %>%
            arrange(Study, Year)
        } else {
          this_table = data.frame(Output="appraisal not found")
        }
    })
    
  },

  options = list(height = 500)
)
```


